---
title: "Trump Tweet Habit Analysis"
author: "Wenlong Yang"
date: "11/3/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this report, I analyzed the tweeting habit of Donald Trump and what we can learn about the president from these tweets.

The data was downloaded from a [website](http://http://www.trumptwitterarchive.com/data/realdonaldtrump/) created by Brendan Brown. I extracted all of Trump's tweets from 2009 to Nov. 3rd 2019 as the total data. The size of the data is about 9 Mb.

```{r import and save data, echo = FALSE, include = FALSE}
library(tidyverse)
library(ggplot2)
library(lubridate)
library(tidyr)

all_tweets <- as_tibble(read.csv("trump_tweets_20191103.csv", stringsAsFactors=FALSE))

all_tweets <- all_tweets %>% mutate(datetime = as_datetime(created_at)) %>% mutate(year = year(datetime), month = month(datetime), day = day(datetime), hour = hour(datetime), minute = minute(datetime))

all_tweets %>% mutate(source = as.factor(source))

ttweets <- all_tweets %>% filter(source %in% c("Twitter for Android","Twitter for iPhone","Twitter Web Client"))


```

## The devices
First of all, let us take a look at the devices Trump use to send tweets. We will look at the statistics for the whole time between 2009 to 2019.

```{r trump tweet devices, echo=FALSE}
ttweets %>% ggplot(aes(source)) + geom_bar() + xlab("Devices") + ggtitle("Fig. 1. Trump tweeting devices")
```

Now, let us check the number of tweets by year.

```{r trump tweet by year, echo=FALSE}
ttweets %>% ggplot(aes(as.character(year), width = 1))+geom_bar() + ggtitle("Fig. 2. Trump tweets by year") + xlab("Year")
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
